si: code and prose exploring Spatial Interaction models

### 2022-04-16 README.qmd
Rename param, shorten code

```{r distance}
library(si)
od = si_to_od(origins = zones, destinations = zones, max_euclidean_distance = 5000)
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
od_res = si_model(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
plot(od_res$distance_euclidean, od_res$res)
```

@@

Perhaps the most important function in the package is therefore `si_to_od()`, which transforms geographic entities (typically zones but points and other geographic features could be used) into a data frame representing the full combination of origin-destination pairs that are less than `max_euclidean_distance` meters apart.
A common saying in data science is that 80% of the effort goes into the pre-processing stage.
This is equally true for spatial interaction modelling as it is for other types of data intensive analysis/modelling work.
So what does this function return?

>>>>

```{r distance}
library(si)
od = si_to_od(origins = zones, destinations = zones, max_dist = 5000)
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
od_res = si_model(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
plot(od_res$distance_euclidean, od_res$res)
```

@@

Perhaps the most important function in the package is therefore `si_to_od()`, which transforms geographic entities (typically zones but points and other geographic features could be used) into a data frame representing the full combination of origin-destination pairs that are less than `max_dist` meters apart.
A common saying in data science is that 80% of the effort goes into the pre-processing stage.
This is equally true for spatial interaction modelling as it is for other types of data intensive analysis/modelling work.
So what does this function return?
